Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
Fix page 3

The PFRA runs primarily as a kernel thread called kswapd. kswapd runs at regular
intervals and sleeps in between. Also, it may be invoked if the system detects
that memory has gone below a threshold. kswapd will continue to run until enough
pages are freed to bring the free memory pool above some threshold before going to
sleep \cite{utlk}.  One concern with systems that have a large memory
usage is that kswapd may expend significant CPU time scanning through hundreds
of thousands of pages.

@@

Assume the memory usage of the rest of the system is $R$. We denote $R_i$ as the
$i$-th measurement of $R$ during a run ($i = 0, 1, ..., 2^{20}$). System memory
usage is known to jitter in Linux \cite{jitter}. To adjust for this jitter, we
define $\Delta_i = R_i - R_0$. For each operation, we take the median value of
$\Delta_i$ across the 5 runs to reduce jitter further.  This is the value
graphed in the figures in the following section. $\Delta_i$ represents the
increase in memory usage due to memory management overheads caused by running
$i$ memory management operations.

>>>>

The PFRA runs primarily as a kernel thread called kswapd. kswapd runs at
regular intervals and sleeps in between. Also, it is invoked if the system
detects that memory has gone below a threshold such as during a page fault.
kswapd will continue to run until enough pages are freed to bring the free
memory pool above some threshold before going to sleep \cite{utlk}.  This may
cause the faulting process to block for a while. One concern with systems that
have a large memory usage is that kswapd may expend significant CPU time
scanning through hundreds of thousands of pages.

@@

Assume the memory usage of the rest of the system is $R$. We denote $R_i$ as
the $i$-th measurement of $R$ during a run ($i = 0, 1, ..., 2^{20}$). $R_0$
corresponds to the measurement before the first operation. System memory usage
is known to jitter in Linux \cite{jitter}. To adjust for this jitter, we define
$\Delta_i = R_i - R_0$. For each operation, we take the median value of
$\Delta_i$ across the 5 runs to reduce jitter further.  This is the value
graphed in the figures in the following section. $\Delta_i$ represents the
increase in memory usage due to memory management overheads caused by running
$i$ memory management operations.
